Kindly Bent to Free Us

### 2018-11-06 kindly/lang.tex
A bit more structure.

\begin{figure*}[h]
  \centering
  \input{syntax}
  \caption{Syntax}
\end{figure*}
% \begin{figure*}[h]
%   \input{semantics}
%   \caption{Reduction rules -- $\ered{I}{E}{e}{v}$ }

% \end{figure*}

>>>>

\subsection{Syntax}

The syntax of \lang is presented in \cref{grammar} and follows
traditional ML languages with let bindings.
Data constructors are introduced by $\app{C}{x}$ and eliminated
with by $\matchin{C}{x}{e}{e'}$.
Types are composed of type variable $\tvar$, parameterized type constructors
$\T{t}$ and arrow types annotated with a kind, noted $\tau \tarr{k} \tau$.
Kinds can be either a kind variable $\kvar$, affine $\kaff$ or unrestricted $kun$.
Type schemes and kind schemes are guarded by a set of constraints.

Environments are composed of value and type bindings, along with type
declarations. Type declarations, of the form
$\tydecl{t}{\kschm}{C}{\tau}$, introduce both a new type constructor $\T{t}$ and
a data constructor $C$.

\begin{figure*}[h]
  \centering
  \input{grammar}
  \caption{Syntax}
  \label{grammar}
\end{figure*}

\subsection{Semantics}

\TODO{}
% \begin{figure*}[h]
%   \input{semantics}
%   \caption{Reduction rules -- $\ered{I}{E}{e}{v}$ }
% \end{figure*}

\subsection{Typing}

\TODO{Add system-F like type rules}

### 2018-11-06 kindly/soa.tex
Blip.
A bit more structure.

\section{The \lang language}

\begin{figure*}[h]
  \centering
  \input{syntax}
  \caption{Syntax}
\end{figure*}
% \begin{figure*}[h]
%   \input{semantics}
%   \caption{Reduction rules -- $\ered{I}{E}{e}{v}$ }

% \end{figure*}

>>>>

\section{Related works}

\subsection{Substructural type systems}

\paragraph{Functional linear of affine type systems}

Alms~\citep{DBLP:conf/popl/TovP11},
F$^\circ$~\citep{DBLP:conf/tldi/MazurakZZ10},
Quill~\citep{DBLP:conf/icfp/Morris16},
Linear Haskell~\citep{DBLP:journals/pacmpl/BernardyBNJS18}

\paragraph{Object systems}
\TODO{}

\subsection{Qualified Types}

HM(X)~\citep{DBLP:journals/tapos/OderskySW99} with extensions to
bounded universal and existentials~\citep{DBLP:conf/icfp/Simonet03}
and GADTs~\citep{DBLP:journals/toplas/SimonetP07},
and syntactic proof of soundness~\citep{DBLP:journals/entcs/SkalkaP02}.

\subsection{Subtyping and constraints}

Flowcaml~\citep{DBLP:conf/popl/PottierS02},
\citet{DBLP:conf/sas/TrifonovS96}.
